Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-09-06 main_paper.tex
Fix weird grammar error in Section 2
Not sure what that last sentence in Section 2 meant to communicate, but it
wasn't pulling it off. I deleted the sentence.

In the next section, we build upon the insight provided by CCT bias-corrected
estimator and propose a simple bootstrap procedure that can directly construct
the robust CIs without requiring the derivation of analytical formulas and
direct estimators for the bias, variance and covariance terms, while relying on
the same first-order bias correction approximation. Assumption~\ref{A2}
requirements are identical to CCT.

>>>>

In the next section, we build upon the insight provided by CCT's bias-corrected
interval and propose a simple bootstrap procedure that can directly construct
the robust CIs without requiring the derivation of analytical formulas and
direct estimators for the bias, variance and covariance terms, while relying on
the same first-order bias correction approximation.
